---
date: 2019-06-07
slug: polisci-research-notes
title: "Research notes in political science journals"
output: html_document
categories:
        - journals
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(rio)
library(tidyverse)
library(kableExtra)

df <- import("data/research_notes.xlsx")
        
```


__The data in this blog post was last updated on 16 October 2024. It previously led to the development of an app that allows users to filter data on political science journals, including different article types. Try it out at <a href='https://resulumit.shinyapps.io/psjournals/'target='_blank'>https://resulumit.shinyapps.io/psjournals</a>__.

In addition to 'regular' articles, some political science journals publish shorter manuscripts as well. They are often called *research notes*, but the name, and indeed the format itself, can differ from one journal to another.<sup><a href='#notes'>1</a></sup> Yet, this definition, by <a href='https://academic.oup.com/poq/pages/general_instructions'target='_blank'>*Public Opinion Quarterly*</a>, covers a lot of common ground:

> Research Notes are shorter reports ... of single findings, important extensions or replications of previous research, or other major additions to the literature that warrant publication, and which can be communicated effectively without the more extended theoretical development or detailed analysis characteristic of regular articles. 

I have gone through the 'author guidelines' of more than three hundred political science journals and put together a list of journals that publish research notes.<sup><a href='#notes'>2</a></sup> You can also click on the hyperlinks under *Format Name* to learn more about the format in each journal.

```{r, table}
df |>  arrange(desc(h5_index), journal) |>
        # add footnotes
        mutate(link = if_else(journal == "Acta Politica", 
                              str_c(link, "<sup><a href='#notes'>3</a></sup>"), 
                               link)
               ) |>
        rename(Journal = journal, "Format Name" = "link",
             Length = length,
             "h5-index" = h5_index) |>
        mutate(Length = str_replace(Length, "--", "&ndash;")) |>
       kable(format = "html", escape = FALSE, align = "l") |>
  kable_styling("striped")

```

## Notes
<p id="notes">[1] For example, the *American Political Science Review* previously had a category called *Letters* for short articles, which has since been removed. However, they still publish shorter manuscripts, with most articles expected to be less than 12,000 words and some even half that length—similar to a research note or letter. For more details, see the journal's <a href="https://www.cambridge.org/core/journals/american-political-science-review/information/author-instructions/preparing-your-materials">submission guidelines</a>.</p>
<p id="notes">[2] Please bear in mind that this is not an exhaustive list and that editorial policies change. If you notice that one or more journals are missing, or that one or more existing entries need updating, please <a href="mailto:resulumit@gmail.com">send me an email</a>. I would be happy to hear from you.</p>
<p id="notes">[3] Research notes are not explicitly mentioned in the journal's guidelines, but the editor has confirmed that they are published, and the guidelines will be updated soon.</p>