---
date: 2021-07-06
slug: polisci-turnaround-acceptance
title: "Turnaround times and acceptance rates at political science journals"
output: html_document
categories:
        - journals
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)

df <- read_csv("2021-turnaround-acceptance/tf_metrics.csv") %>% 
        mutate(acceptance_rate = as.numeric(str_remove(acceptance_rate, "%")))
        

```


It would be great if <a href="https://resulumit.shinyapps.io/psjournals/" target="_blank">the psjournals app</a> included information on turnaround times and acceptance rates at political science journals. This is one of the most common feedback that I receive from its users, and I could not agree more.

These statistics are unfortunately unavailable for many journals.

The journals published by Taylor & Francis are now a welcome exception. The publisher has recently started to provide statistics on journal turnaround times and acceptance rates on its website --- in separate sections for individual journals. 

This blogpost brings these statistics together, collecting the data with the code <a href="https://gist.github.com/resulumit/05f5186f2c7abd7efed0e05bc64a358e" target="_blank">available on GitHub</a>.

All turnaround times indicate the median, measured in days. Hover over the column headers for their definitions. Furhter details are available on <a href="https://authorservices.taylorandfrancis.com/publishing-your-research/choosing-a-journal/journal-metrics/#" target="_blank">the publisher's website</a>. 

See also the graphs that summarise the statistics [at the end of the post](#descriptive-graphs).

<br>

|Journal| <span class="cname" title="Median number of days, from submission to first decision, including desk rejections">First Decision</span>|<span class="cname" title="Median number of days, from submission to first decision, excluding desk rejections">Post-PR Decision</span>|<span class="cname" title="Median number of days, from acceptance to online publication">Online Publication</span>|Acceptance Rate|
|-------:|--:|--:|--:|--:|
|<a href='https://www.tandfonline.com/toc/rjpp20/current'>Journal of European Public Policy</a>|3|47|21|24%|
|<a href='https://www.tandfonline.com/toc/cjms20/current'>Journal of Ethnic and Migration Studies</a>|23|79|21|14%|
|<a href='https://www.tandfonline.com/toc/fwep20/current'>West European Politics</a>|39|68|27|18%|
|<a href='https://www.tandfonline.com/toc/rrip20/current'>Review of International Political Economy</a>|10|86|19|24%|
|<a href='https://www.tandfonline.com/toc/fenp20/current'>Environmental Politics</a>|76|99|18|18%|
|<a href='https://www.tandfonline.com/toc/fdem20/current'>Democratization</a>|15|41|20|34%|
|<a href='https://www.tandfonline.com/toc/cnpe20/current'>New Political Economy</a>|18|89|15|22%|
|<a href='https://www.tandfonline.com/toc/upcp20/current'>Political Communication</a>|17|75|38|12%|
|<a href='https://www.tandfonline.com/toc/uter20/current'>Studies in Conflict and Terrorism</a>|||18||
|<a href='https://www.tandfonline.com/toc/ftpv20/current'>Terrorism and Political Violence</a>|41|62|27|20%|
|<a href='https://www.tandfonline.com/toc/fses20/current'>South European Society and Politics</a>|||35||
|<a href='https://www.tandfonline.com/toc/geui20/current'>Journal of European Integration</a>|54|121|28|28%|
|<a href='https://www.tandfonline.com/toc/rglo20/current'>Globalizations</a>|17|105|23|53%|
|<a href='https://www.tandfonline.com/toc/fgeo20/current'>Geopolitics</a>|33|87|22|30%|
|<a href='https://www.tandfonline.com/toc/rpsa20/current'>Post-Soviet Affairs</a>|32|78|12|14%|
|<a href='https://www.tandfonline.com/toc/ccst20/current'>Citizenship Studies</a>|23|102|12|15%|
|<a href='https://www.tandfonline.com/toc/flgs20/current'>Local Government Studies</a>|27|76|15|20%|
|<a href='https://www.tandfonline.com/toc/csms20/current'>Social Movement Studies</a>|56|126|11|23%|
|<a href='https://www.tandfonline.com/toc/rwaq20/current'>Washington Quarterly</a>|||30||
|<a href='https://www.tandfonline.com/toc/feus20/current'>European Security</a>|29|54|19|37%|
|<a href='https://www.tandfonline.com/toc/crea20/current'>Review of African Political Economy</a>|40|104|45|22%|
|<a href='https://www.tandfonline.com/toc/fsst20/current'>Security Studies</a>|34|103|22|6%|
|<a href='https://www.tandfonline.com/toc/rtep20/current'>Territory, Politics, Governance</a>|52|94|32|30%|
|<a href='https://www.tandfonline.com/toc/fmed20/current'>Mediterranean Politics</a>|9|86|15|25%|
|<a href='https://www.tandfonline.com/toc/mppc20/current'>Problems of Post-Communism</a>|88|108|41|39%|
|<a href='https://www.tandfonline.com/toc/rfjp20/current'>International Feminist Journal of Politics</a>|59|118|38|36%|
|<a href='https://www.tandfonline.com/toc/fcsp20/current'>Contemporary Security Policy</a>|4|47|15|12%|
|<a href='https://www.tandfonline.com/toc/fjss20/current'>Journal of Strategic Studies</a>|0|88|19|17%|
|<a href='https://www.tandfonline.com/toc/rbul20/current'>Bulletin of the Atomic Scientists</a>|||37||
|<a href='https://www.tandfonline.com/toc/gini20/current'>International Interactions</a>|49|64|31|24%|
|<a href='https://www.tandfonline.com/toc/ccpo20/current'>Contemporary Politics</a>|11|77|14|22%|
|<a href='https://www.tandfonline.com/toc/cjhr20/current'>Journal of Human Rights</a>|19|80|65|28%|
|<a href='https://www.tandfonline.com/toc/ccam20/current'>Cambridge Review of International Affairs</a>|54|85|21|27%|
|<a href='https://www.tandfonline.com/toc/fjcs21/current'>East European Politics</a>|52|86|14|41%|
|<a href='https://www.tandfonline.com/toc/fcri20/current'>Critical Review of International Social and Political Philosophy</a>|42|101|9|50%|
|<a href='https://www.tandfonline.com/toc/fbep20/current'>Journal of Elections, Public Opinion and Parties</a>|56|72|15|23%|
|<a href='https://www.tandfonline.com/toc/fjls20/current'>Journal of Legislative Studies</a>|73|86|21|53%|
|<a href='https://www.tandfonline.com/toc/cjss20/current'>Journal of Southern African Studies</a>|||30||
|<a href='https://www.tandfonline.com/toc/fgrp20/current'>German Politics</a>|80|91|20|44%|
|<a href='https://www.tandfonline.com/toc/fint20/current'>Intelligence and National Security</a>|||11||
|<a href='https://www.tandfonline.com/toc/reno20/current'>Ethnopolitics</a>|28|57|22|62%|
|<a href='https://www.tandfonline.com/toc/mijp20/current'>International Journal of Political Economy</a>|||58||
|<a href='https://www.tandfonline.com/toc/wwap20/current'>Journal of Women, Politics and Policy</a>|0|90|59|10%|
|<a href='https://www.tandfonline.com/toc/cajp20/current'>Australian Journal of Political Science</a>|32|76|15|36%|
|<a href='https://www.tandfonline.com/toc/rrep20/current'>Representation</a>|70|92|21|46%|
|<a href='https://www.tandfonline.com/toc/rcri20/current'>Critical Review</a>|||45||
|<a href='https://www.tandfonline.com/toc/cjgr20/current'>Journal of Genocide Research</a>|16|80|20|33%|
|<a href='https://www.tandfonline.com/toc/upse20/current'>Journal of Political Science Education</a>|88|102|18|58%|
|<a href='https://www.tandfonline.com/toc/cnid20/current'>National Identities</a>|63|117|24|41%|
|<a href='https://www.tandfonline.com/toc/fmes20/current'>Middle Eastern Studies</a>|13||27|29%|
|<a href='https://www.tandfonline.com/toc/rcfp20/current'>Canadian Foreign Policy Journal</a>|12|47|40|51%|
|<a href='https://www.tandfonline.com/toc/ujic20/current'>International Journal of Intelligence and CounterIntelligence</a>|||53||
|<a href='https://www.tandfonline.com/toc/cper20/current'>Peace Review</a>|||98||
|<a href='https://www.tandfonline.com/toc/fdas20/current'>Democracy and Security</a>|57|72|22|37%|
|<a href='https://www.tandfonline.com/toc/ucst20/current'>Comparative Strategy</a>|||50||
|<a href='https://www.tandfonline.com/toc/fisa20/current'>Israel Affairs</a>|||10||
|<a href='https://www.tandfonline.com/toc/rpic20/current'>Journal of Policing, Intelligence and Counter Terrorism</a>|2|133|14|23%|
|<a href='https://www.tandfonline.com/toc/rnpr20/current'>Nonproliferation Review</a>|41|57|48|42%|
|<a href='https://www.tandfonline.com/toc/vpps20/current'>Perspectives on Political Science</a>|147|102|23|33%|
|<a href='https://www.tandfonline.com/toc/rpnz20/current'>Political Science</a>|56|84|28|27%|
|<a href='https://www.tandfonline.com/toc/rasi20/current'>Asian Journal of Political Science</a>|52|64|14|19%|
|<a href='https://www.tandfonline.com/toc/caji20/current'>Australian Journal of International Affairs</a>|5|45|15|24%|
|<a href='https://www.tandfonline.com/toc/rifa20/current'>Israel Journal of Foreign Affairs</a>|||26||
|<a href='https://www.tandfonline.com/toc/rper20/current'>Parliaments, Estates and Representation</a>|||21||
|<a href='https://www.tandfonline.com/toc/rfia20/current'>Review of Faith and International Affairs</a>|||56||
|<a href='https://www.tandfonline.com/toc/rsaj20/current'>South African Journal of International Affairs</a>|2|90|22|49%|

<br>

### Descriptive graphs

Here are two graphs that describe the data in the table above. The first is for the statistics on speed while the latter plots the acceptance variable. 

```{r, turnaround}

df %>% pivot_longer(cols = first_decision:online_publication,
                    names_to = "type", values_to = "statistic") %>%
        mutate(type = factor(type, levels = c("first_decision", "first_review", "online_publication"),
                              labels = c("First Decision", "Post-PR Decision", "Online Publication"))) %>% 
        ggplot(aes(x = statistic, color = type, fill = type)) +
        geom_density(alpha = 0.3) +
        theme_light() +
        labs(y = "Density\n", x = "\nDays") +
        theme(panel.background = element_rect(fill = "#faf9f9"),
              plot.background = element_rect(fill = "#faf9f9"),
              legend.background = element_rect(fill = "#faf9f9"),
              axis.line = element_line(colour = "black", size = 0.25),
              panel.grid.major = element_line(colour = "grey95", size = 0.25),
              panel.grid.minor = element_line(colour = "grey95", size = 0.125),
              panel.border = element_rect(fill = NA, colour = "grey95", size = 0.25),
              plot.title = element_text(lineheight = .8, hjust = 0),
              strip.text = element_text(colour = "black", size=11),
              strip.background = element_rect(fill= "faf9f9", color= "faf9f9"),
              legend.position = "bottom",
              legend.title = element_blank()) +
        scale_fill_discrete(name = "") +
        scale_color_discrete(name = "")


```

<br>

```{r, acceptance}

df %>% ggplot(aes(x = acceptance_rate)) +
        geom_density(alpha = 0.3) +
        theme_light() +
        labs(y = "Density\n", x = "\nAcceptance Rate") +
        theme(panel.background = element_rect(fill = "#faf9f9"),
              plot.background = element_rect(fill = "#faf9f9"),
              legend.background = element_rect(fill = "#faf9f9"),
              axis.line = element_line(colour = "black", size = 0.25),
              panel.grid.major = element_line(colour = "grey95", size = 0.25),
              panel.grid.minor = element_line(colour = "grey95", size = 0.125),
              panel.border = element_rect(fill = NA, colour = "grey95", size = 0.25),
              plot.title = element_text(lineheight = .8, hjust = 0),
              strip.text = element_text(colour = "black", size=11),
              strip.background = element_rect(fill= "faf9f9", color= "faf9f9"),
              legend.position = "bottom",
              legend.title = element_blank())


```


<style type="text/css">

.cname {
    border-bottom: 1px dotted;
}

</style>