---
date: 2024-11-15
slug: polisci-replication-studies
title: "Replication studies in political science journals"
output: html_document
categories:
    - journals
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

library(rio)
library(tidyverse)
library(kableExtra)

df_metrics <- import("data/psjournals_source_forwebsite.xlsx", which = "journal_metrics") |>
        select(id, h5_index)

df <- import("data/psjournals_source_forwebsite.xlsx") |>
        left_join(df_metrics, by = "id") |>
        filter(str_detect(type, "Replic")) |>
        mutate( 
                # hyperlink journal names
                journal = paste0("<a href='", url, "' target='_blank'>", journal, "</a>"),
                # create word limits
                word_limit = case_when(
                        is.na(lower_limit) & is.na(upper_limit) ~ "*NA*",
                        is.na(lower_limit) & limit_unit == "words" ~ paste0(as.integer(upper_limit / 1000), "k words"),
                        is.na(lower_limit) & limit_unit == "pages" ~ paste0(upper_limit, " pages")
                )
        ) |>
        select(journal, h5_index, type, word_limit)
        
```

Replication studies play a critical role in advancing knowledge and ensuring the robustness of findings. Some journals are increasingly recognising this by introducing dedicated article categories for replication studies. These categories provide a clear pathway for researchers to share their work replicating and scrutinising existing studies, fostering transparency, and improving the reliability of published research.

At least seven political science journals now publish a specific article type for replication studies. All accept replication submissions focused on articles previously published in their own journal or in other relevant outlets. Other journals may accept replication studies under different categories, such as [Research Notes](https://resulumit.com/blog/polisci-research-notes/), but the list below highlights those with a dedicated replication category.

```{r, table}
df |>  arrange(desc(h5_index), journal) |>
        # add footnotes
        rename(Journal = journal, "Format Name" = type,
             "Length Limit" = word_limit,
             "h5-index" = h5_index) |>
       kable(format = "html", escape = FALSE, align = "l") |>
  kable_styling("striped")

```


This list is sourced from my [political science journals app](https://resulumit.shinyapps.io/psjournals/), which you may also find useful for exploring additional article types and journal options.
