---
date: 2024-11-20
slug: polisci-review-articles
title: "Review articles in political science journals"
output: html_document
categories:
    - journals
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

library(rio)
library(tidyverse)
library(kableExtra)

df_metrics <- import("data/psjournals_source_forwebsite.xlsx", which = "journal_metrics") |>
        select(id, h5_index)

df <- import("data/psjournals_source_forwebsite.xlsx") |>
        left_join(df_metrics, by = "id") |>
        filter(type_category == "review") |>
        mutate( 
                # hyperlink journal names
                journal = paste0("<a href='", url, "' target='_blank'>", journal, "</a>"),
                # create word limits
                word_limit = case_when(
                        is.na(lower_limit) & is.na(upper_limit) ~ "*NA*",
                        is.na(lower_limit) & !is.na(upper_limit) ~ paste0(upper_limit, " ", limit_unit),
                        !is.na(lower_limit) & !is.na(upper_limit) ~ paste0(lower_limit, " -- ", upper_limit, " ", limit_unit),
                )
        ) |>
        select(journal, h5_index, type, word_limit)
        
```

Review articles remain an important part of academic publishing, and this is certainly true in political science, where `r length(unique(df$journal))` journals publish them. These include a variety of article types under this broad category, such as state-of-the-field reviews, literature surveys, and review essays. While author guidelines differ, these articles typically summarise key publications or developments, highlight gaps in the literature, and propose directions for future research.

The table below identifies journals in political science that explicitly categorise and publish review articles, demonstrating the diversity of formats available for this essential academic contribution.It is sourced from my [political science journals app](https://resulumit.shinyapps.io/psjournals/), which you may also find useful for exploring additional article types and journal options.

```{r, table}
df |>  arrange(desc(h5_index), journal) |>
        # add footnotes
        rename(Journal = journal, "Format Name" = type,
             "Length Limit" = word_limit,
             "h5-index" = h5_index) |>
       kable(format = "html", escape = FALSE, align = "l") |>
  kable_styling("striped")

```

